Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-07-09 thirdPaper/draft/typeConeAssociahedra.tex
ask for schematic diagram

>>>>

Schematic diagram:\yann{Vincent, Arnau, je suis certain que vous feriez bien mieux que moi. Puis-je vous demander de le représenter ?}

I.1 explains the type cone approach to the problem

This strategy is used in I.2.2 for cluster algebras and in I.2.3 for gentle algebras.

II.3 cluster categories (2-Calabi--Yau triangulated categories) is used in 1.2.2

II.4 generalises II.3, and offers a different proof for I.2.3
